Supplimentary materials

### 2020-10-15 supplimentary_tables.Rmd
Update following reviewers comments

---
title: 
output: 
  pdf_document:
    keep_tex: yes
header-includes:
  - \usepackage{float} 
  - \usepackage{longtable}
  - \pagenumbering{gobble}
  - \usepackage{caption}
  - \captionsetup[table]{labelformat=empty}
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "supplimentary") })
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacman::p_load(tidyverse, knitr, kableExtra, qwraps2, brms, broom.mixed, bnlearn)

source("r-files/functions.R")
source("r-files/methods_code.R")
source("r-files/results_code.R")
```

@@

\textbf{S4 Table. Probabilities of injury conditional on the variables in the Markov blanket for injured\_1.}

@@

tab3 <- newprobtable(
  tallc,
  c("balance_1", "stiffness_1", "nlelg_1", "hours", "clevel"),
  "injured_1",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>% 
  select(7, 2:6) %>% 
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>% 
  mutate_all(~str_replace_all(., "_", "\\\\_"))

@@

\textbf{S5 Table. Probabilities of injury conditional on the variables in the Markov blanket for injured\_2.}

@@

tab4 <- newprobtable(
  tallc,
  c("balance_2", "stiffness_2", "nlelg_2", "FFFS_1", "hrv_2"),
  "injured_2",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>%
  select(7, 2:6) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_"))

@@

\textbf{S6 Table. Highest and lowest probability of injury, conditional on the all variables in the Markov blanket for ``injured''.}

>>>>

---
title: 
output: 
  pdf_document:
    keep_tex: yes
header-includes:
  - \usepackage{float} 
  - \usepackage{longtable}
  - \pagenumbering{gobble}
  - \usepackage{caption}
  - \captionsetup[table]{labelformat=empty}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "supplimentary") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacman::p_load(tidyverse, knitr, kableExtra, qwraps2, brms, broom.mixed, bnlearn, janitor)

# source("r-files/functions.R")
# source("r-files/methods_code.R")
# source("r-files/results_code.R")
load("all_data2.RData")
```

@@

\textbf{S4 Table. Breakdown of injury count by sport and injury type (chronic or acute)}

```{r results = 'asis'}

injtable %>% 
  left_join(datanet %>% 
              select(id, sportg, time), c("id", "time")) %>% 
  tabyl(sportg, acu_over) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  select(sport = sportg, everything()) %>% 
  mutate(across(.fns = ~str_replace(.x, "%", "\\\\%"))) %>% 
  kable(
    caption = "",
    escape = F,
    format = "latex",
    align = "lcc"
  ) %>% 
  kable_styling(latex_options = ("HOLD_position"))
```

\newpage
\blandscape

\textbf{S5 Table. Breakdown of injury count by sport and injury location}

```{r results = 'asis'}

injtable %>% 
  left_join(datanet %>% 
              select(id, sportg, time), c("id", "time")) %>% 
  mutate(bodypart = ifelse(bodypart %in% c("foot_toe", "ankle_achilles"), "foot_ankle", bodypart)) %>% 
  tabyl(sportg, bodypart) %>% 
  adorn_totals() %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  select(sport = sportg,  
         `foot / ankle` = foot_ankle, 
         `lower leg` = lowerleg, 
         knee,
         `upper leg` = upperleg, 
         hip, 
         torso, 
         `upper arm / shoulder` = upperarm_shoulder,
         `elbow / lower arm` = elbow_lowerarm_hand, 
         `head / neck` = head_neck) %>% 
  mutate(across(.fns = ~str_replace(.x, "%", "\\\\%"))) %>% 
  kable(
    caption = "",
    escape = F,
    format = "latex",
    align = "lccccccccc"
  ) %>% 
  kable_styling(latex_options = ("HOLD_position"))
```

\elandscape

\textbf{S6 Table. Probabilities of injury conditional on the variables in the Markov blanket for injured\_1.}

@@

tab3 <- newprobtable(
  tallc,
  c("balance_1", "stiffness_1", "NLE_1", "hours", "clevel"),
  "injured_1",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>% 
  select(7, 2:6) %>% 
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>% 
  mutate_all(~str_replace_all(., "_", "\\\\_"))

@@

\textbf{S7 Table. Probabilities of injury conditional on the variables in the Markov blanket for injured\_2.}

@@

tab4 <- newprobtable(
  tallc,
  c("balance_2", "stiffness_2", "NLE_2", "FFFS_1", "HRV_2"),
  "injured_2",
  "injured",
  avg30
) %>%
  arrange(-prob) %>%
  select(outcome, everything()) %>%
  dendroTools::round_df(2) %>%
  select(7, 2:6) %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_"))

@@

\textbf{S8 Table. Highest and lowest probability of injury, conditional on the all variables in the Markov blanket for ``injured''.}
